### 2017-10-24 abstract.tex
first commit, abstract added

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
\usepackage{caption}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\usepackage[a4paper]{geometry}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\newcommand\invisiblesection[1]{%
  \refstepcounter{section}%
  \addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}%
  \sectionmark{#1}}

\title{
\normalfont \normalsize
\huge Technology-based aids for people affected by Autism Spectrum Disorder (ASD)  \\ % The assignment title
}

\author{Davide Peron, Cristina Gava}
\date{\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

Individuals affected by Autism Spectrum Disorder(ASD) are often unable to communicate in an
appropriate way, they show strong difficulties in social interactions and in manifesting their affective
states.
The conventional techniques, used to improve the performances of these people in the
everyday tasks, are observation-based and can require a lot of effort in terms of time and money, with limited
results.
Technology-assisted teraphies can result more powerful and fast.

Our aim is to analyze the current technology-based solutions that can help therapists in the treatment
of people affected by ASD.
These solutions exploit the joint use of human intelligence and artificial intelligence to improve
the powerfulness of therapies and to allow a better integration of these individuals in the society.
Examples of these type of aids are Virtual Assistants and Agents as therapeutic tools,
wearable technologies or VR headset to help them in everyday communication and to improve their
fundamental and social skills.
An interesting field that can be analyzed is the use of robotic avatar instead of a therapist, in order to increase
the usefulness of a therapy, improving the response and the interaction time of the disabled user.

\end{document}

### 2017-11-14 paper.tex
Set template and started intruduction

% \documentclass[journal]{IEEEtran}
\documentclass[12pt,journal,draftclsnofoot,onecolumn]{IEEEtran}
\IEEEoverridecommandlockouts

% remove colon after subsubsection, use spacing instead
\makeatletter
\renewcommand{\@IEEEsectpunct}{\quad}
\makeatother

\makeatletter
% add a small spacing *before* subsections
\let\origsubsubsection\subsubsection
\renewcommand\subsubsection{\@ifstar{\starsubsubsection}{\nostarsubsubsection}}

\newcommand\nostarsubsubsection[1]
{\subsubsectionprelude\origsubsubsection{#1}}

\newcommand\subsubsectionprelude{%
  \vspace{6pt}
}
\makeatother

% change default font to charter
% \usepackage{charter}
% \usepackage[bitstream-charter]{mathdesign}
% \usepackage{XCharter}
\usepackage{amsfonts}

% Fixing IEEEtran.cls bug with [english]{babel}
\makeatletter
\def\markboth#1#2{\def\leftmark{\@IEEEcompsoconly{\sffamily}\MakeUppercase{\protect#1}}%
\def\rightmark{\@IEEEcompsoconly{\sffamily}\MakeUppercase{\protect#2}}}
\makeatother

% \usepackage{t1enc}

\usepackage{listings}
\usepackage{multirow}
%\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\selectlanguage{english}
\usepackage{color}
%\usepackage{caption}
\usepackage{cite}
\usepackage[pdftex]{graphicx}

% \usepackage{subfig}
\usepackage{subcaption}
\usepackage{amsmath}

\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\usepackage{amsfonts}
\usepackage{array}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{url}
\usepackage{enumerate}
\usepackage{multirow}

\usepackage{siunitx}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{multicol}% http://ctan.org/pkg/multicols
\usepackage[font=footnotesize]{caption}
% \usepackage[font=scriptsize]{subcaption}
% Tikz
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\pgfplotsset{plot coordinates/math parser=false}
\newlength\fheight
\newlength\fwidth
\usetikzlibrary{patterns,decorations.pathreplacing,backgrounds,calc}
\definecolor{SchoolColor}{RGB}{0.71, 0, 0.106}%181,0,27} unipd red
\definecolor{chaptergrey}{rgb}{0.61, 0, 0.09} % dialed back a little
\definecolor{midgrey}{rgb}{0.4, 0.4, 0.4}
\definecolor{chaptergreen}{rgb}{0.09, 0.612, 0}
\definecolor{chapterpurple}{rgb}{0.522, 0, 0.612}
\definecolor{chapterlightgreen}{rgb}{0, 0.612, 0.522}

%\raggedbottom

% Pseudocode
\usepackage[ruled, vlined]{algorithm2e}

\SetKwRepeat{Do}{do}{while}
\SetKwBlock{wpPa}{with probability $P_A$}{end}
\DontPrintSemicolon
% \usepackage{algorithm}
% \usepackage[noend]{algpseudocode}
% \renewcommand\algorithmicthen{}
% \renewcommand\algorithmicdo{}
\usepackage{lscape}

\addto\captionsenglish{\renewcommand{\figurename}{Fig.}}

\newcommand{\field}[1]{\mathbb{#1}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\renewcommand{\arraystretch}{2}

\newcommand{\DP}[1]{\textcolor{blue}{\textbf{(DP says: #1)}}}
\newcommand{\cri}[1]{\textcolor{violet}{\textbf{(Cri says: #1)}}}

\usepackage{threeparttable}
%\usepackage[table,xcdraw]{xcolor}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{booktabs}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\usepackage{array, blindtext}
\usepackage{wrapfig}
\usepackage{pdfpages}
\usepackage[acronym]{glossaries}

% use tikArchiviz images or eps
\newif\iftikz
\tikztrue

\graphicspath{{./figures/}}

\title{Technology-based aids for people affected by Autism Spectrum Disorder (ASD)}
\author{\IEEEauthorblockN{Cristina Gava, Peron Davide}\\
\small{{Department of Information Engineering, University of Padova -- Via Gradenigo, 6/b, 35131 Padova, Italy\\
Email: {\tt\{gavacris, perondav\}@dei.unipd.it}\\}}
}

% Reduce the space below figs.
%\setlength{\belowcaptionskip}{-0.7cm}

\renewcommand{\equationautorefname}{Eq.}

%% Glossary
\newacronym{asd}{ASD}{Autism Spectrum Disorder}

\glsresetall
\begin{document}

\def\equationautorefname~#1\null{(#1)\null}
\setlength{\belowcaptionskip}{-0.2cm}

% reduce space after title
\makeatletter
\patchcmd{\@maketitle}
  {\addvspace{0.5\baselineskip}\egroup}
  {\addvspace{-1.2\baselineskip}\egroup}
  {}
  {}
\makeatother

\maketitle

\begin{abstract}
Individuals affected by Autism Spectrum Disorder(ASD) are often unable to communicate in an
appropriate way, they show strong difficulties in social interactions and in manifesting their affective
states.
The conventional techniques, used to improve the performances of these people in the
everyday tasks, are observation-based and can require a lot of effort in terms of time and money, with limited
results.
Technology-assisted teraphies can result more powerful and fast.

Our aim is to analyze the current technology-based solutions that can help therapists in the treatment
of people affected by ASD.
These solutions exploit the joint use of human intelligence and artificial intelligence to improve
the powerfulness of therapies and to allow a better integration of these individuals in the society.
Examples of these type of aids are Virtual Assistants and Agents as therapeutic tools,
wearable technologies or VR headset to help them in everyday communication and to improve their
fundamental and social skills.
An interesting field that can be analyzed is the use of robotic avatar instead of a therapist, in order to increase
the usefulness of a therapy, improving the response and the interaction time of the disabled user.
\end{abstract}

\glsresetall
\section{Introduction} \label{sec:introduction}

% TODO Brief presentation of ASD (?)
\gls{asd} is a term used to cover a very big set of disorders. In this field there are a lot of studies and experiments, but still is one of the most unknown \DP{forse unknown non è il massimo come termine qui} disease. The symptoms are well known, while the causes are mostly unknown. Nowadays, \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered on a patient at least 3 years old. For this reason, several techniques have been studied to wonder if a children has this disorder in the first 2 years of life.
% TODO Main technologies available until now

\section{Technical Approach}
\label{sec:tech_approach}

\subsection{Simulated Annealing}

\subsection{Jumping Ball}
\subsection{Genetic Algorithm}

\section{Conclusions And Future Work}\label{sec:conclusions}

\bibliographystyle{IEEEtran}
\bibliography{bibliography}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2017-11-14 abstract.tex

@@
 
-\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text
+\setlength\parindent{10pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text
 
@@
 
-Individuals affected by Autism Spectrum Disorder(ASD) are often unable to communicate in an
+Individuals affected by Autism Spectrum Disorder(ASD), especially the not-verbal ones, are often unable to communicate in an
 appropriate way, they show strong difficulties in social interactions and in manifesting their affective
-states.
+states or their necessities.
 The conventional techniques, used to improve the performances of these people in the
@@
 results.
-Technology-assisted teraphies can result more powerful and fast.
+Technology-assisted therapies can result more powerful and fast.
 
-Our aim is to analyze the current technology-based solutions that can help therapists in the treatment
-of people affected by ASD.
+Our aim is to analyze the current technology-based solutions that can help the therapist and the family of an autistic subject to interact with him.
 These solutions exploit the joint use of human intelligence and artificial intelligence to improve
@@
 fundamental and social skills.
-An interesting field that can be analyzed is the use of robotic avatar instead of a therapist, in order to increase
-the usefulness of a therapy, improving the response and the interaction time of the disabled user.
+
+Interesting example fields that can be analyzed are:
+\begin{itemize}
+\item the use of robotic avatar instead of a therapist in order to improve the response and interaction time of the disabled user;
+\item a wearable IoT device to collect data about interaction among children with ASD in classroom settings;
+\item an autonomous computer system for training social orientation skills to young children with ASD.
+\end{itemize}
 

### 2017-11-15 paper.tex
Started section 1

@@
 \newacronym{asd}{ASD}{Autism Spectrum Disorder}
+\newacronym{va}{VA}{Virtual Agents}
 
@@
 \begin{abstract}
-Individuals affected by Autism Spectrum Disorder(ASD) are often unable to communicate in an
+Individuals affected by Autism Spectrum Disorder(ASD), especially the not-verbal ones, are often unable to communicate in an
 appropriate way, they show strong difficulties in social interactions and in manifesting their affective
-states.
+states or their necessities.
 The conventional techniques, used to improve the performances of these people in the
@@
 results.
-Technology-assisted teraphies can result more powerful and fast.
+Technology-assisted therapies can result more powerful and fast.
 
-Our aim is to analyze the current technology-based solutions that can help therapists in the treatment
-of people affected by ASD.
+Our aim is to analyze the current technology-based solutions that can help the therapist and the family of an autistic subject to interact with him.
 These solutions exploit the joint use of human intelligence and artificial intelligence to improve
 the powerfulness of therapies and to allow a better integration of these individuals in the society.
-Examples of these type of aids are Virtual Assistants and Agents as therapeutic tools,
-wearable technologies or VR headset to help them in everyday communication and to improve their
-fundamental and social skills.
-An interesting field that can be analyzed is the use of robotic avatar instead of a therapist, in order to increase
-the usefulness of a therapy, improving the response and the interaction time of the disabled user.
 \end{abstract}
@@
 For this reason, several techniques have been studied to wonder if a children has this disorder in the first 2 years of life.
-% TODO Main technologies available until now
 
-\section{Technical Approach}
-\label{sec:tech_approach}
+In this respect, this work is divided in two main sections.
+In \autoref{sec:thera_tech} we present some innovative tool to improve social skills of a child affected by ASD faster than a classical face-to-face therapy will does \DP{Questa frase fa schifo}.
+In \autoref{sec:every_tech} we present a couple of wearable products that allow a faster and easier integration of the subject in the everydays tasks.
 
-\subsection{Simulated Annealing}
+\section{Therapeutical techniques}
+\label{sec:thera_tech}
+
+The classical way to conduct a therapy session, is a face-to-face meeting between the subject and the therapist.
+Usually, is conducted in four phases: the first one is called \textit{Instruction}, in which the therapist explain what is the skill that the subject is going to learn; the second one is the \textit{Modeling} phase, in which the therapist show the patient what he has to do; there is then the \textit{Rehearsal} phase, in which the patient tries to imitate the therapist and finally a \textit{Feedback} phase in which the therapist draw its own conclusions about the test.
+The problem of this kind of therapy are the completely subjective evaluation procedure carried out by the therapist and that the subject's attention is not immediate.
+
+%TODO Avatar-based techniques to improve the performances of the therapy
+%TODO Methods to detect the anxiety level
+To improve the performances of the sessions, the use of \gls{va} has been introducted.
+
+\section{Everydays tools techniques}
+\label{sec:every_tech}
 

### 2017-11-16 paper.tex
Started avatar section

@@
 \usepackage{listings}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage{url}
@@
 \author{\IEEEauthorblockN{Cristina Gava, Peron Davide}\\
-\small{{Department of Information Engineering, University of Padova -- Via Gradenigo, 6/b, 35131 Padova, Italy\\
-Email: {\tt\{gavacris, perondav\}@dei.unipd.it}\\}}
+\small{{Neurosensorial Engineering final project\\
+A.A. 2017/2018\\}}
 }
@@
 \end{abstract}
+\begin{IEEEkeywords}
+\centering
+Autism Spectrum Disorder, Avatar-robots, Wearable Technology, Health Monitoring
+\end{IEEEkeywords}
+\clearpage
+
+\tableofcontents
+\clearpage
 
@@
 To improve the performances of the sessions, the use of \gls{va} has been introducted.
+\gls{va} consist of an Avatar, that can be a robot or a virtual character, a learning software that receive information from the Avatar, elaborate them and adjust the response of the Avatar, and an interface for the therapist to interpretate the results.
+In a \gls{va} session, the therapist, with the aids of the learning software, learns the Avatar in order to do an action that the child has to imitate, the child tries to imitate the Avatar learning new way to interact with the society.
+Different system has been proposed, we propose here two different solutions, one more general and one more complex and efficient.
+
+\subsection{General AVATAR idea}
+\label{sec:avatar_general}
+The idea of an Avatar-based therapy session is proposed firstly in \cite{Guerrero-vasquez}. They propose a
 
@@
 
-\section{Conclusions And Future Work}\label{sec:conclusions}
+\section{Conclusions}\label{sec:conclusions}
 
 \bibliographystyle{IEEEtran}
-\bibliography{bibliography}
+\bibliography{IEEEabrv,bibliography}
 
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2017-11-16 paper.tex
Advance in first section

@@
 \newacronym{va}{VA}{Virtual Agents}
+\newacronym{dof}{DoF}{Degrees of Freedom}
 
@@
 %TODO Methods to detect the anxiety level
-To improve the performances of the sessions, the use of \gls{va} has been introducted.
-\gls{va} consist of an Avatar, that can be a robot or a virtual character, a learning software that receive information from the Avatar, elaborate them and adjust the response of the Avatar, and an interface for the therapist to interpretate the results.
+To improve the performances of the sessions, the use of \gls{va} platforms has been introducted.
+A \gls{va} platform consist of an avatar, that can be a robot or a virtual character, a learning software that receive information from the Avatar, elaborate them and adjust the response of the Avatar, and an interface for the therapist to interpretate the results.
 In a \gls{va} session, the therapist, with the aids of the learning software, learns the Avatar in order to do an action that the child has to imitate, the child tries to imitate the Avatar learning new way to interact with the society.
@@
 \label{sec:avatar_general}
-The idea of an Avatar-based therapy session is proposed firstly in \cite{Guerrero-vasquez}. They propose a
+
+\begin{figure}[h]
+\centering
+
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{avatar_system.png}
+\caption{Scheme of AVATAR system}
+\label{fig:avatar_scheme}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{avatar_tasks.png}
+\caption{Structure of AVATAR platform}
+\label{fig:avatar_tasks}
+\end{minipage}
+
+\end{figure}
+
+The idea of an Avatar-based therapy session is proposed firstly in \cite{Guerrero-vasquez}.
+They propose a system composed by a \gls{va} and an \textit{expert system} used by the therapist to instruct the \gls{va}.
+A general scheme of the proposed system is shown in \autoref{fig:avatar_scheme}.
+
+They chose to use a Virtual Agent instead of a robot since, according with the needs, it provides the possibility to customize the tool, while a robot is limitated on its shape and its \gls{dof}.
+
+As can be seen in \autoref{fig:avatar_tasks}, the platform is organized as follow:
+\begin{LaTeXdescription}
+	\item[Child Interface] It selects the child's favourite Virtual Agent and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
+	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the Virtual Agent, it stores the scenario and features of the Virtual Agent and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
+	\item[Therapist Interface] Allow the therapist to access to the reports generated by the Expert System and gives information about the current therapy, in order to allow the therapist to draw conclusions.
+\end{LaTeXdescription}
+
+The key point is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
+Since the VA that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist who promotes the interaction in combination with the expert system.
 

### 2017-11-16 paper.tex
Finish part about first paper

@@
 
-The key point is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
+The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he's put in front of them.
+The character can be not strictly a human, since the highest degree of affinity can be towards an animal or an object.
+
+The key point in their work is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
 Since the VA that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist who promotes the interaction in combination with the expert system.
+
+\subsection{A more complex system}
+\label{sec:avatar_complex}
+
+Another more complex and complete approach was performed in \cite{Alahbabi17}, using a robot instead of a \gls{va}, since it has been shown in \cite{Pioggia08} that patients show a more favorable response towards humanoid robots than to other non-humanoid virtual characters.
+
+This approach has sensible advantages but also some intrinsic shortcomings:
+\begin{itemize}
+	\item most of the robotic or virtualized therapy are preprogrammed, that make the session boring and repetitive;
+	\item robots are limited and work in a controlled environment;
+	\item usually robots don't have a quantitative behavioral analysis tool due to the absence of therapists during their development process.
+\end{itemize}
 

### 2017-11-16 paper.tex
Added title section
Finished second paper part

@@
 
+In this work they try to fulfill these lacks using a set of advance technology tools, specifically a \textit{NAO Robot} (visible in \autoref{fig:nao_robot}) and a Perception Neuron Set of 32 sensors.
+
+In their proposal, the robot will replace the therapist in the room.
+The therapist would wear portable motion sensors giving him a partial control of the robot motion, and receive a visual and auditory stream from the robot.
+The therapist would also be able to talk to the child through the robot, by using a robotic voice.
+
+\begin{figure}[h]
+\centering
+
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{nao_robot.png}
+\caption{Scheme of AVATAR system}
+\label{fig:nao_robot}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{scores.png}
+\caption{Structure of AVATAR platform}
+\label{fig:scores}
+\end{minipage}
+
+\end{figure}
+
+The strength of this work is that the robot behavior can be adapted based on the degree of involvment of the child in the session.
+Indeed, as the session starts, a low number of \gls{dof} are given to the robot, in order makes the child imitate a set of very simple movements.
+As the user progresses in the engagement (we'll see later that this means take more points), more \gls{dof} are given to the robot, usually enabling disabled actuators, in order to increase the complexity of the movements.
+
+During the whole process a heart-rate measuring band is worn by the partecipant, to monitor the partecipant's level of anxiety and stop or change the session whenever an intervention is required.
+
+To monitor the actual movements performed by the child, a Microsoft Kinect is used.
+
+The movements performed by the robot and imitated by the child are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.
+
+During the session, points are given to the child as they progress and perform the right movement at the right time.
+The total score is given by the sum of three contributes:
+
+\begin{LaTeXdescription}
+	\item[Motion Score] Is relative to the goodness of the movement made by the patient to imitate the robot;
+	\item[Attention Score] the child takes one point for each second the child was looking at the robot’s face whenever the robot was asking the child a question;
+	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and moment in which the child started answering the questions.
+The child is given 10 points for the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
+\end{LaTeXdescription}
+
+After 20 minutes of session therapy, results are collected.
+This experiment has been done in five healthy male children and with three different type of interaction subject: an avatar programmed as just said, a pre-programmed robot and a therapist in a classical face-to-face session.
+Score has been collected for each type of interaction and the results are shown in \autoref{fig:scores}.
+
+As we can see the performance of the avatar are initially almost equal to the ones of a pre-programmed robot, but along the session, child get bored of the last one due to its repetitive movements and requirements, while the score with the avatar increase due to its continuous adaption to the child needs.
+The score collected with a real therapist are sensible lower at the beginning and it increase along the session since the therapist adapt to the child needs.
 \section{Everydays tools techniques}

### 2017-11-16 paper.tex
Correct some typos

--- 2017-11-16 paper.tex
@@
 To improve the performances of the sessions, the use of \gls{va} platforms has been introducted.
-A \gls{va} platform consist of an avatar, that can be a robot or a virtual character, a learning software that receive information from the Avatar, elaborate them and adjust the response of the Avatar, and an interface for the therapist to interpretate the results.
-In a \gls{va} session, the therapist, with the aids of the learning software, learns the Avatar in order to do an action that the child has to imitate, the child tries to imitate the Avatar learning new way to interact with the society.
+A \gls{va} platform consist of an avatar, that can be a robot or a virtual character, a learning software that receives information from the Avatar, elaborates them and adjusts the response of the Avatar, and an interface for the therapist to interpretate the results.
+In a \gls{va} session, the therapist, with the aids of the learning software, learns the Avatar in order to do an action that the child has to imitate, the child tries to imitate the Avatar, learning new way to interact with the society.
+
 Different system has been proposed, we propose here two different solutions, one more general and one more complex and efficient.
@@
 
-They chose to use a Virtual Agent instead of a robot since, according with the needs, it provides the possibility to customize the tool, while a robot is limitated on its shape and its \gls{dof}.
+They chose to use a \gls{va} instead of a robot since, according with the needs, it provides the possibility to customize the tools it offers and its appearance, while a robot is limitated on its shape and its \gls{dof}.
 
@@
 \begin{LaTeXdescription}
-	\item[Child Interface] It selects the child's favourite Virtual Agent and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
-	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the Virtual Agent, it stores the scenario and features of the Virtual Agent and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
+	\item[Child Interface] It selects the child's favourite \gls{va} and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
+	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the \gls{va}, it stores the scenario and features of the chosen \gls{va} and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
 	\item[Therapist Interface] Allow the therapist to access to the reports generated by the Expert System and gives information about the current therapy, in order to allow the therapist to draw conclusions.
@@
 
-The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he's put in front of them.
+The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he's put in front of one of them.
 The character can be not strictly a human, since the highest degree of affinity can be towards an animal or an object.
 
-The key point in their work is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
-Since the VA that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist who promotes the interaction in combination with the expert system.
+The key point in their work is that the information received on the screen of the Therapist Interface shows a real time image of the child and the monitored progress statistics.
+Since the \gls{va} that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist in combination with the expert system who promotes the interaction.
 
@@
 \begin{itemize}
-	\item most of the robotic or virtualized therapy are preprogrammed, that make the session boring and repetitive;
+	\item most of the robotic or virtualized therapies are pre-programmed, that make the session boring and repetitive;
 	\item robots are limited and work in a controlled environment;
@@
 \end{itemize}
+
+In this work they try to fulfill these lacks using a set of advanced technology tools, specifically a \textit{NAO Robot} (visible in \autoref{fig:nao_robot}) and a Perception Neuron Set of 32 sensors.
+
+In their proposal, the robot will replace the therapist in the room.
+The therapist would wear portable motion sensors giving him a partial control of the robot motion, and he would receive a visual and auditory stream from the robot.
+The therapist would also be able to talk to the child through the robot, by using a robotic voice.
+
+\begin{figure}[h]
+\centering
+
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{nao_robot.png}
+\caption{Scheme of AVATAR system}
+\label{fig:nao_robot}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{scores.png}
+\caption{Structure of AVATAR platform}
+\label{fig:scores}
+\end{minipage}
+
+\end{figure}
+
+The strength of this work is that the robot behavior can be adapted based on the degree of engagement of the child in the session.
+Indeed, as the session starts, a low number of \gls{dof} are given to the robot, in order to makes the child imitate a set of very simple movements.
+As the patient progresses in the engagement (we'll see later that this means take more points), more \gls{dof} are given to the robot, usually enabling disabled actuators, in order to increase the complexity of the movements.
+
+During the whole process a heart-rate measuring band is worn by the partecipant, to monitor the partecipant's level of anxiety and stop or change the session whenever an intervention is required.
+
+To monitor the actual movements performed by the child, a Microsoft Kinect is used.
+
+The movements performed by the robot and imitated by the child are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.
+
+During the session, points are given to the child as he progresses and performs the right movement at the right time.
+The total score is given by the sum of three contributes:
+
+\begin{LaTeXdescription}
+	\item[Motion Score] Is relative to the goodness of the movement made by the patient to imitate the robot;
+	\item[Attention Score] the child takes one point for each second he's looking at the robot’s face whenever the robot is asking him a question;
+	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and moment in which the child start answering the questions.
+	10 points are given for the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
+\end{LaTeXdescription}
+
+After 20 minutes of session therapy, results are collected.
+This experiment has been done in five healthy male children and with three different type of interaction subject: an avatar programmed as said before, a pre-programmed robot and a therapist in a classical face-to-face session.
+Score has been collected for each type of interaction and the results are shown in \autoref{fig:scores}.
+
+As we can see the performance of the avatar are initially almost equal to the ones of a pre-programmed robot, but along the session, child gets bored of the last one due to its repetitive movements and requirements, while the score with the avatar increases due to its continuous adaption to the child needs.
+The scores collected with a real therapist are very lower at the beginning compared with the first two type of interaction and it increases along the session since the therapist adapts the requirements to the child needs.
 

### 2017-11-16 paper.tex
Added frist part on hand eye coordination

--- 2017-11-16 paper.tex
@@
 The classical way to conduct a therapy session, is a face-to-face meeting between the subject and the therapist.
-Usually, is conducted in four phases: the first one is called \textit{Instruction}, in which the therapist explain what is the skill that the subject is going to learn; the second one is the \textit{Modeling} phase, in which the therapist show the patient what he has to do; there is then the \textit{Rehearsal} phase, in which the patient tries to imitate the therapist and finally a \textit{Feedback} phase in which the therapist draw its own conclusions about the test.
+Usually, it is conducted in four phases: the first one is called \textit{Instruction}, in which the therapist explains what is the skill that the subject is going to learn; the second one is the \textit{Modeling} phase, in which the therapist shows the patient what he has to do; there is then the \textit{Rehearsal} phase, in which the patient tries to imitate the therapist and finally a \textit{Feedback} phase in which the therapist draws its own conclusions about the test.
 The problem of this kind of therapy are the completely subjective evaluation procedure carried out by the therapist and that the subject's attention is not immediate.
@@
 
+\section{Diagnostic techniques}
+\label{sec:diagnosis}
+
+\subsection{Hand-eye coordination}
+\label{sec:hand_eye}
+A different aspect to take into consideration when facing subjects with ASD, is the motor disorder related to the syndrome.
+In \cite{Casellato2017} a new approach to face the issue is presented, where the proposed protocol may be used for ad hoc subject training, helping children with ASD to enhance motor abilities related to hand-eye coordination.
+
+Moreover, although normally it is not considered as a diagnostic criteria, motor impairment associated with ASD may have a significant impact on daily life tasks and, since up to 80\% of children with autism show motor anomalies highly correlated with the severity of social deficiency, hand-eye coordination could be considered as a new early diagnostic strategy for ASD syndrome \cite{Casellato2017}.
+In fact, it has been suggested that sensory integration with bad timing brings to poor motor performance in children with ASD: the task of integrating multisensory input influences the forming of coherent perception, action coordination and planning.
+Nowadays, the normal procedure to assess this motor coordination deficiency is the clinical observation and self-report questionnaires, so a new non-invasive objective method to map the development of ASD such hand-eye motor performance, could be a powerful diagnostic tool.
+
+\subsubsection{Material and methods}
+In \cite{Casellato2017} the experimental set-up involved sixteen children aged between 8 and 10 years old and was composed by a haptic robotic manipulandum (Phantom Omni, Sensable-Geomagic) with a 3D printed pen-like handle, a control pc with a suited control algorithm running and a table-mounted screen Eye tracker T60 (Tobii) of $1280\times1024$ pixels.
+The manipulandum's sampling frequency was of 1 kHz, while the Eye Tracker's sampling frequency was of 60 Hz.
+
+Prior to the beginning of the trial, a brief amount of time was given to the children in order to familiarize with the system.
+
+The actual trial consisted in two main tasks: the first task was about following a diagonal straight path moving an end-effector from a start square to an end square without exiting the path boundaries; in the second task a target moved on the screen following a curvilinear predefined path representing a digitalized version of the visuo-motor precision sub-task of the NEPSY-II protocol.
+
+During the first task, a primary amount of attempts was done without applying external force disturbance to the pen-like handle; the attempts that followed, instead, were perturbed by an external force, while the final ones were not perturbed again.
+Results from this task show that:
+\begin{itemize}
+\item the task was fulfilled pretty well in the first unperturbed part;
+\item during the first perturbed attempts the performance of the subjects were significantly low and attest a slow adaptation to the change;
+\item after some perturbed attempts the subjects eventually manage to compensate the force almost properly, with a progressive reduction in the product $pathL \dot T$ (where $pathL$ is the length of the path while $T$ is the time taken to travel through it);
+\item when the attempts go back to be not-perturbated there is an initial overcompensation, which eventually is re-calibrated with even better performance than the ones obtained initially.
+\end{itemize}
+
+Figures \ref{task1} and \ref{task1_pT} show the results just described.
+
+\begin{figure}[h]
+\centering
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{task1.png}
+\caption{Task 1 path following}
+\label{fig:task1}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{task1_pT.png}
+\caption{Task 1 pathLxT vs n of trials}
+\label{fig:task1_pT}
+\end{minipage}
+\end{figure}
+
 \section{Everydays tools techniques}

### 2017-11-17 paper.tex
Concluded first part in diagnostic

@@
 \newacronym{dof}{DoF}{Degrees of Freedom}
+\newacronym{td}{TD}{Typically-Developing}
 
@@
 \gls{asd} is a term used to cover a very big set of disorders.
-In this field there are a lot of studies and experiments, but still is one of the most unknown \DP{forse unknown non è il massimo come termine qui} disease.
-The symptoms are well known, while the causes are mostly unknown.
-Nowadays, \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered on a patient at least 3 years old.
-For this reason, several techniques have been studied to wonder if a children has this disorder in the first 2 years of life.
+There are a lot of studies and experiments in this field, but still a lot questions about it are unresolved \DP{forse unknown non è il massimo come termine qui} \cri{Prova a vedere se così ti piace}: for example, the symptoms are well known, while the causes are still mostly unknown.
+Nowadays \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered to a patient who is at least 3 years old.
+For this reason, several techniques have been studied in order to establish if a children has this disorder in the first 2 years of life.
 
-In this respect, this work is divided in two main sections.
-In \autoref{sec:thera_tech} we present some innovative tool to improve social skills of a child affected by ASD faster than a classical face-to-face therapy will does \DP{Questa frase fa schifo}.
-In \autoref{sec:every_tech} we present a couple of wearable products that allow a faster and easier integration of the subject in the everydays tasks.
-
-\section{Therapeutical techniques}
-\label{sec:thera_tech}
-
-The classical way to conduct a therapy session, is a face-to-face meeting between the subject and the therapist.
-Usually, it is conducted in four phases: the first one is called \textit{Instruction}, in which the therapist explains what is the skill that the subject is going to learn; the second one is the \textit{Modeling} phase, in which the therapist shows the patient what he has to do; there is then the \textit{Rehearsal} phase, in which the patient tries to imitate the therapist and finally a \textit{Feedback} phase in which the therapist draws its own conclusions about the test.
-The problem of this kind of therapy are the completely subjective evaluation procedure carried out by the therapist and that the subject's attention is not immediate.
-
-%TODO Avatar-based techniques to improve the performances of the therapy
-%TODO Methods to detect the anxiety level
-To improve the performances of the sessions, the use of \gls{va} platforms has been introducted.
-A \gls{va} platform consist of an avatar, that can be a robot or a virtual character, a learning software that receive information from the Avatar, elaborate them and adjust the response of the Avatar, and an interface for the therapist to interpretate the results.
-In a \gls{va} session, the therapist, with the aids of the learning software, learns the Avatar in order to do an action that the child has to imitate, the child tries to imitate the Avatar learning new way to interact with the society.
-Different system has been proposed, we propose here two different solutions, one more general and one more complex and efficient.
-
-\subsection{General AVATAR idea}
-\label{sec:avatar_general}
-
-\begin{figure}[h]
-\centering
-
-\begin{minipage}{0.48\textwidth}
-\centering
-\includegraphics[width=\textwidth]{avatar_system.png}
-\caption{Scheme of AVATAR system}
-\label{fig:avatar_scheme}
-\end{minipage}
-\begin{minipage}{0.48\textwidth}
-\centering
-\includegraphics[width=\textwidth]{avatar_tasks.png}
-\caption{Structure of AVATAR platform}
-\label{fig:avatar_tasks}
-\end{minipage}
-
-\end{figure}
-
-The idea of an Avatar-based therapy session is proposed firstly in \cite{Guerrero-vasquez}.
-They propose a system composed by a \gls{va} and an \textit{expert system} used by the therapist to instruct the \gls{va}.
-A general scheme of the proposed system is shown in \autoref{fig:avatar_scheme}.
-
-They chose to use a Virtual Agent instead of a robot since, according with the needs, it provides the possibility to customize the tool, while a robot is limitated on its shape and its \gls{dof}.
-
-As can be seen in \autoref{fig:avatar_tasks}, the platform is organized as follow:
-\begin{LaTeXdescription}
-	\item[Child Interface] It selects the child's favourite Virtual Agent and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
-	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the Virtual Agent, it stores the scenario and features of the Virtual Agent and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
-	\item[Therapist Interface] Allow the therapist to access to the reports generated by the Expert System and gives information about the current therapy, in order to allow the therapist to draw conclusions.
-\end{LaTeXdescription}
-
-The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he's put in front of them.
-The character can be not strictly a human, since the highest degree of affinity can be towards an animal or an object.
-
-The key point in their work is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
-Since the VA that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist who promotes the interaction in combination with the expert system.
-
-\subsection{A more complex system}
-\label{sec:avatar_complex}
-
-Another more complex and complete approach was performed in \cite{Alahbabi17}, using a robot instead of a \gls{va}, since it has been shown in \cite{Pioggia08} that patients show a more favorable response towards humanoid robots than to other non-humanoid virtual characters.
-
-This approach has sensible advantages but also some intrinsic shortcomings:
-\begin{itemize}
-	\item most of the robotic or virtualized therapy are preprogrammed, that make the session boring and repetitive;
-	\item robots are limited and work in a controlled environment;
-	\item usually robots don't have a quantitative behavioral analysis tool due to the absence of therapists during their development process.
-\end{itemize}
+With respect to these aims, this work is divided into two main sections: In \autoref{sec:diagnosis} we present some innovative tools and procedures to help diagnosing the syndrome in the first one or two years of a child; in \autoref{sec:thera_tech} we describe three \cri{vedere se poi il numero va bene} devices and methods useful for learning and improving cognitive skills.
 
@@
 \label{sec:hand_eye}
-A different aspect to take into consideration when facing subjects with ASD, is the motor disorder related to the syndrome.
+A different aspect to take into consideration when facing subjects with \gls{asd}, is the motor disorder related to the syndrome.
 In \cite{Casellato2017} a new approach to face the issue is presented, where the proposed protocol may be used for ad hoc subject training, helping children with ASD to enhance motor abilities related to hand-eye coordination.
@@
 
-Figures \ref{task1} and \ref{task1_pT} show the results just described.
+Figures \ref{fig:task1} and \ref{fig:task1_pT} show the results just described.
 
@@
 
-\section{Everydays tools techniques}
-\label{sec:every_tech}
+During the second task there is a significant difference between \gls{td} (TD) children and children with ASD and between the first and the second attempt:
+\begin{itemize}
+\item Even though there is not a strong correlation among the children of a same group, it can be noticed that both TD children and ASD children performed better during the second attempt, when they already knew the path to follow a priori;
+\item In general, \gls{td} children had better performance than \gls{asd} children;
+\item For ASD children, the \textit{hand-gaze} distance was higher than for TD children, but quite the same in both the attempts.
+\end{itemize}
 
-\subsection{Jumping Ball}
-\subsection{Genetic Algorithm}
+Figure \ref{path} shows an example of trial with a TD child.
+
+\begin{figure}
+\centering
+\includegraphics[width = .55\textwidth]{path.png}
+\caption{Trials A and B for a \gls{td} child}
+\label{path}
+\end{figure}
+
+\subsubsection{summary observations}
+\label{sec:summary}
+
+The experiment results can be summarized with a few crucial conclusions:
+\begin{itemize}
+\item the first task showed how children with \gls{asd} took longer to learn the task execution correctly, even though once the process had been assimilated the execution was correct, this meaning that these children showed a delayed ability to learn from sensory prediction errors; moreover the ASD child had more variability in motor execution, this suggesting more difficulty in maintaining performance consistency, and the gaze pattern was sticking less to the hand pattern if compared to the \gls{td} children.
+\item the second task showed how children with ASD obtained performance slightly worse than the TD children, but anyway they were able deploy the information regarding the previously assimilated path to improve the performance.
+This suggests that gls{asd} children are able to take advantage of the availability of the whole motor plan and supports the hypothesis that simple motor planning is intact but there is a diminished use of feedback.
+\end{itemize}
+
+From these results, since the timing (which is strictly associated with adaptation and prediction) is one of the crucial aspects managed by the cerebellum (known to be the cerebral section reporting the most consistent brain differences in autism), it can be supported the hypothesis that bad timing in sensory integration causes degraded motor performance and delayed learning in children with \gls{asd}.
+
+Such dysfunctions could affect not only motor processes but also cognitive ones, and this form of motor tracking could also be useful to better understand the mechanism at the basis of the well-documented visuo-motor impairments in ASD (\cite{Chow2010}, \cite{Green2013}, \cite{Papa}) and throw more light on the functional integrity of brain networks during development in people with ASD.
+
+\section{Therapeutical techniques}
+\label{sec:thera_tech}
+
+The classical way to conduct a therapy session is a face-to-face meeting between the subject and the therapist.
+Usually, it is conducted in four phases: the first one is called \textit{Instruction}, in which the therapist explains what is the skill that the subject is going to learn; the second one is the \textit{Modeling} phase, in which the therapist shows the patient what he has to do; then there is the \textit{Rehearsal} phase, in which the patient tries to imitate the therapist, and finally a \textit{Feedback} phase in which the therapist draws its own conclusions about the test.
+The problem of this kind of therapy structure is the completely subjective evaluation procedure carried out by the therapist and the non-immediate subject's attention.
+
+%TODO Avatar-based techniques to improve the performances of the therapy
+%TODO Methods to detect the anxiety level
+To improve the performance of the sessions, the use of \gls{va} platforms has been introducted.
+A \gls{va} platform consists of an avatar, that can be a robot or a virtual character, a learning software that receives information from the Avatar, elaborates them and adjusts the response of the Avatar, and an interface for the therapist that interprets the results.
+In a \gls{va} session the therapist, with the aids of the learning software, trains the Avatar to do an action that the child has to imitate.
+At the same time, the child tries to imitate the Avatar learning new ways to interact with the society.
+Different system has been proposed, we describe here two different solutions, one more general and one more complex and efficient.
+
+\subsection{General AVATAR idea}
+\label{sec:avatar_general}
+
+\begin{figure}[h]
+\centering
+
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{avatar_system.png}
+\caption{Scheme of AVATAR system}
+\label{fig:avatar_scheme}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{avatar_tasks.png}
+\caption{Structure of AVATAR platform}
+\label{fig:avatar_tasks}
+\end{minipage}
+
+\end{figure}
+
+The idea of an Avatar-based therapy session is shown firstly in \cite{Guerrero-vasquez}.
+In the paper they propose a system composed by a \gls{va} and an \textit{expert system} used by the therapist to instruct the \gls{va}.
+A general scheme of the system is shown in \autoref{fig:avatar_scheme}.
+
+They chose to use a Virtual Agent instead of a robot since, according with the needs, it provides the possibility to customize the tool, while a robot is limited by its structure and its \gls{dof}.
+
+As can be seen in \autoref{fig:avatar_tasks}, the platform is organized as follows:
+\begin{LaTeXdescription}
+	\item[Child Interface] It selects the child's favorite Virtual Agent and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
+	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the Virtual Agent, it stores the scenario and features of the Virtual Agent and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
+	\item[Therapist Interface] Allow the therapist to access to the reports generated by the Expert System and gives information about the current therapy, in order to allow the therapist to draw conclusions.
+\end{LaTeXdescription}
+
+The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he is put in front of them.
+It is not necessary for the character to be a human, since the highest degree of affinity can be towards an animal or an object.
+
+The key point in this work is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
+Since the VA that the child observes on his screen is his therapist in disguise, actually it is the therapist who, combined with artificial intelligence, promotes the interaction in combination with the expert system.
+
+\subsection{A more complex system}
+\label{sec:avatar_complex}
+
+Another more complex and complete approach was performed in \cite{Alahbabi17}, using a robot instead of a \gls{va}; this because it has been shown in \cite{Pioggia08} that patients manifest a more favorable response towards humanoid robots than to other non-humanoid virtual characters.
+
+This approach has sensible advantages but also some intrinsic shortcomings:
+\begin{itemize}
+	\item most of the robotic or virtualized therapies are preprogrammed and this makes the session boring and repetitive;
+	\item robots are limited and work in a controlled environment;
+	\item usually robots do not have a quantitative behavioral analysis tool, due to the absence of therapists during their development process.
+\end{itemize}
 

### 2017-11-21 paper.tex
Fixed floating figures

@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 
+In this work they try to fulfill these lacks using a set of advanced technology tools, specifically a \textit{NAO Robot} (visible in \autoref{fig:nao_robot}) and a Perception Neuron Set of 32 sensors.
+
+In their proposal, the robot will replace the therapist in the room.
+The therapist would wear portable motion sensors giving him a partial control of the robot motion, and he would receive a visual and auditory stream from the robot.
+The therapist would also be able to talk to the child through the robot, by using a robotic voice.
+
+\begin{figure}[h]
+\centering
+
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{nao_robot.png}
+\caption{Scheme of AVATAR system}
+\label{fig:nao_robot}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\centering
+\includegraphics[width=\textwidth]{scores.png}
+\caption{Structure of AVATAR platform}
+\label{fig:scores}
+\end{minipage}
+
+\end{figure}
+
+The strength of this work is that the robot behavior can be adapted based on the degree of engagement of the child in the session.
+Indeed, as the session starts, a low number of \gls{dof} are given to the robot, in order to makes the child imitate a set of very simple movements.
+As the patient progresses in the engagement (we'll see later that this means take more points), more \gls{dof} are given to the robot, usually enabling disabled actuators, in order to increase the complexity of the movements.
+
+During the whole process a heart-rate measuring band is worn by the partecipant, to monitor the partecipant's level of anxiety and stop or change the session whenever an intervention is required.
+
+To monitor the actual movements performed by the child, a Microsoft Kinect is used.
+
+The movements performed by the robot and imitated by the child are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.
+
+During the session, points are given to the child as he progresses and performs the right movement at the right time.
+The total score is given by the sum of three contributes:
+
+\begin{LaTeXdescription}
+	\item[Motion Score] Is relative to the goodness of the movement made by the patient to imitate the robot;
+	\item[Attention Score] the child takes one point for each second he's looking at the robot’s face whenever the robot is asking him a question;
+	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and moment in which the child start answering the questions.
+	10 points are given for the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
+\end{LaTeXdescription}
+
+After 20 minutes of session therapy, results are collected.
+This experiment has been done in five healthy male children and with three different type of interaction subject: an avatar programmed as said before, a pre-programmed robot and a therapist in a classical face-to-face session.
+Score has been collected for each type of interaction and the results are shown in \autoref{fig:scores}.
+
+As we can see the performance of the avatar are initially almost equal to the ones of a pre-programmed robot, but along the session, child gets bored of the last one due to its repetitive movements and requirements, while the score with the avatar increases due to its continuous adaption to the child needs.
+The scores collected with a real therapist are very lower at the beginning compared with the first two type of interaction and it increases along the session since the therapist adapts the requirements to the child needs.
+
 \section{Conclusions}\label{sec:conclusions}

### 2017-11-21 paper.tex
Checked introduction

@@
 \gls{asd} is a term used to cover a very big set of disorders.
-There are a lot of studies and experiments in this field, but still a lot questions about it are unresolved \DP{forse unknown non è il massimo come termine qui} \cri{Prova a vedere se così ti piace}: for example, the symptoms are well known, while the causes are still mostly unknown.
+There are a lot of studies and experiments in this field, but still a lot questions about it are unresolved: for example, the symptoms are well known, while the causes are still mostly unknown.
 Nowadays \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered to a patient who is at least 3 years old.

### 2017-11-21 paper.tex
Added part on EEG

--- 2017-11-17 paper.tex
@@
 \usepackage{amsfonts}
+\usepackage{diagbox}
 
@@
 \newacronym{td}{TD}{Typically-Developing}
+\newacronym{eeg}{EEG}{Electro Encephalography}
+\newacronym{roc}{ROC}{Receiver Operating Characteristic}
 
@@
 
+\subsection{Abnormalities in Connectivity of EEG activity}
+\label{sec:EEG}
+
+In 1943 a first case of an autistic person developing epilepsy was described.
+Since then, multiple cases have been registered and so researchers started to look for associations between abnormal \gls{eeg} findings and individuals with \gls{asd}.
+This field is still mostly to be uncovered, since classification and evaluation of \gls{eeg} signals are limited for now, but recent studies suggest a feasible use of this diagnostic technique in the field of gls{asd} \cite{Behnam2008}.
+
+If we unify the knowledge on the \gls{eeg} functioning principles, to the signal processing theory, we obtain a powerful diagnostic tool: representations based on Fourier Transform have been commonly applied and this brought to light that the \gls{eeg} spectrum contains five main frequency bands with characteristic waveforms and so the main way to highlight differences between normal subjects and autistic subjects can be to analyze the coherence of \gls{eeg} signals form different brain regions in order to find coupling among the signals in frequency domain.
+
+\subsubsection{Example of procedure}
+\label{sec:procEEG}
+
+In \cite{Behnam2008} the authors describe a trial done on 10 children with \gls{asd} and a control group of 9 age-matched control subjects that have not suffered from neurological disorder.
+From the 21 scalp loci of the international $10 - 20$ system the EEG signals were recorded, the subjects were in a relaxed state with the eyes open and more than 10 minutes of data were collected for each child.
+
+The signal processing passage consisted in low-pass filtering at 100 Hz, subsequent sampling at 256 Hz and digitization through 12-bit ADC.
+Finally.
+EEG signals were divided into 3 artifact-free epochs, subsequently filtered trough a Hamming window FIR band-pass filter.
+
+With the signal set in this way the Fourier Transform has been applied, using a Gaussian time window in order to observe sections in which the signal is seen as stationary.
+
+The last passage was the estimation of coherence variables: MSC is the estimated coherence range (it goes form 0 to 1) and is obtained from auto and cross-power spectra of the channels.
+
+To evaluate the statistical difference between the control group's signals and the ones from the \gls{asd} children group, the authors used one-way analysis of variance tests, while to measure the discriminating ability of the test they used \gls{roc} plots.
+Moreover, to classify between \gls{asd} subjects and control subjects, nearest neighbor classifier has been used.
+
+\subsubsection{results}
+\label{sec:discussion}
+
+Results show that the discriminating ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and table \ref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
+Moreover, figure \ref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.
+
+\begin{table}
+\centering
+\begin{tabular}[h]{c|cc}
+\toprule
+\diagbox{Cases}{Membership} & Autism & Normal\\
+\midrule
+Autism & 90.0 & 10.0\\
+Normal & 11.1 & 88.9\\
+\bottomrule
+\end{tabular}
+\caption{Table of confusion for the correct group discrimination using STFT-BW}
+\label{tab:prediction}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width = .5\textwidth]{head.png}
+\caption{Results of coherence values and connectivity in channels brain}
+\label{fig:head}
+\end{figure}
+
 \section{Therapeutical techniques}

### 2017-11-22 paper.tex
Commit di prova per usare git

@@
 
-Results show that the discriminating ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and table \ref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
+Results show that the discriminating \cri{Commento prova per usare git} ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and table \ref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
 Moreover, figure \ref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.

### 2017-11-22 paper.tex
Removed commento di prova and fix some typo

--- 2017-11-21 paper.tex
@@
 
-\subsubsection{results}
+\subsubsection{Results}
 \label{sec:discussion}
 
-Results show that the discriminating ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and table \ref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
-Moreover, figure \ref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.
+Results show that the discriminating ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and \autoref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
+Moreover, \autoref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.
 

### 2017-11-23 paper.tex
Removed AVATAR general section and integrated the other

--- 2017-11-21 paper.tex
@@
 To improve the performance of the sessions, the use of \gls{va} platforms has been introducted.
-A \gls{va} platform consists of an avatar, that can be a robot or a virtual character, a learning software that receives information from the Avatar, elaborates them and adjusts the response of the Avatar, and an interface for the therapist that interprets the results.
+A \gls{va} platform consists of an Avatar, that can be a robot or a virtual character, a learning software that receives information from the Avatar, elaborates them and adjusts the response of the Avatar, and an interface for the therapist that interprets the results.
 In a \gls{va} session the therapist, with the aids of the learning software, trains the Avatar to do an action that the child has to imitate.
 At the same time, the child tries to imitate the Avatar learning new ways to interact with the society.
-Different system has been proposed, we describe here two different solutions, one more general and one more complex and efficient.
 
-\subsection{General AVATAR idea}
-\label{sec:avatar_general}
+Different system has been proposed, we describe here two solutions based on an Avatar, the first is a robotic one while the second is virtual and adapts the tasks proposed in function of the child's anxiety level.
 
-\begin{figure}[h]
-\centering
+\subsection{Robotic-based therapy}
+\label{sec:robotic}
 
-\begin{minipage}{0.48\textwidth}
-\centering
-\includegraphics[width=\textwidth]{avatar_system.png}
-\caption{Scheme of AVATAR system}
-\label{fig:avatar_scheme}
-\end{minipage}
-\begin{minipage}{0.48\textwidth}
-\centering
-\includegraphics[width=\textwidth]{avatar_tasks.png}
-\caption{Structure of AVATAR platform}
-\label{fig:avatar_tasks}
-\end{minipage}
+The first solution was proposed in \cite{Alahbabi17}, using a robotic Avatar.
+They chose a robotic-based solution since it has been shown in \cite{Pioggia08} that patients manifest a more favorable response towards humanoid robots than to other non-humanoid virtual characters.
 
-\end{figure}
-
-The idea of an Avatar-based therapy session is shown firstly in \cite{Guerrero-vasquez}.
-In the paper they propose a system composed by a \gls{va} and an \textit{expert system} used by the therapist to instruct the \gls{va}.
-A general scheme of the system is shown in \autoref{fig:avatar_scheme}.
-
-They chose to use a Virtual Agent instead of a robot since, according with the needs, it provides the possibility to customize the tool, while a robot is limited by its structure and its \gls{dof}.
-
-As can be seen in \autoref{fig:avatar_tasks}, the platform is organized as follows:
-\begin{LaTeXdescription}
-	\item[Child Interface] It selects the child's favorite Virtual Agent and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
-	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the Virtual Agent, it stores the scenario and features of the Virtual Agent and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
-	\item[Therapist Interface] Allow the therapist to access to the reports generated by the Expert System and gives information about the current therapy, in order to allow the therapist to draw conclusions.
-\end{LaTeXdescription}
-
-The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he is put in front of them.
-It is not necessary for the character to be a human, since the highest degree of affinity can be towards an animal or an object.
-
-The key point in this work is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
-Since the VA that the child observes on his screen is his therapist in disguise, actually it is the therapist who, combined with artificial intelligence, promotes the interaction in combination with the expert system.
-
-\subsection{A more complex system}
-\label{sec:avatar_complex}
-
-Another more complex and complete approach was performed in \cite{Alahbabi17}, using a robot instead of a \gls{va}; this because it has been shown in \cite{Pioggia08} that patients manifest a more favorable response towards humanoid robots than to other non-humanoid virtual characters.
-
-This approach has sensible advantages but also some intrinsic shortcomings:
+This approach has sensible advantages if compared with classical therapies, but it has also some intrinsic shortcomings:
 \begin{itemize}
@@
 
-The movements performed by the robot and imitated by the child are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.
+The movements performed by the robot and imitated by the child and the therapist's questions are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.
 
-During the session, points are given to the child as he progresses and performs the right movement at the right time.
+During the session, points are given to the child as he progresses and performs the right movement at the right time or if he gives an acceptable answer to a question.
 The total score is given by the sum of three contributes:
@@
 \begin{LaTeXdescription}
-	\item[Motion Score] Is relative to the goodness of the movement made by the patient to imitate the robot;
+	\item[Motion Score] is relative to the goodness of the movement made by the patient to imitate the robot;
 	\item[Attention Score] the child takes one point for each second he's looking at the robot’s face whenever the robot is asking him a question;

### 2017-11-25 paper.tex
Added part on Anxiety test

--- 2017-11-22 paper.tex
@@
 \newcommand{\DP}[1]{\textcolor{blue}{\textbf{(DP says: #1)}}}
-\newcommand{\cri}[1]{\textcolor{violet}{\textbf{(Cri says: #1)}}}
+\newcommand{\cri}[1]{\textcolor{yellow}{\textbf{(Cri says: #1)}}}
 
@@
 \newacronym{roc}{ROC}{Receiver Operating Characteristic}
+\newacronym{as}{AS}{Anxiety-Sensitive}
+\newacronym{ps}{PS}{Performance-Sensitive}
+\newacronym{pr}{PR}{Pulse Rate}
+\newacronym{eda}{EDA}{Electrodermal Activity}
+\newacronym{skt}{SKT}{Skin Temperature}
 
@@
 
+\subsection{Physiology-sensitive VR-based platform}
+\label{sec:anxiety}
+
+Anxiety is a condition that usually characterizes the subjects with \gls{asd} and has bad effects on educational training, but often it is hard for the therapist to recognize it and properly intervene to reduce it.
+Several studies show that physiological signals can be evoked by different stimuli in an environment with the presence of a VR, and normally the transition from a relaxed state to an anxiety state manifests through the activation of the Autonomous Nervous System.
+In particular, for the case of anxiety the physiology biomakers can be for example the heart rate increase, increase of conductance in tonic activity in skin or decrease of skin temperature.
+All these changes can be registered and interpreted by a computer.
+
+Kuriakose et al.
+in \cite{Kuriakose2017} presented a new interactive and didactic-training tool in which the anxiety level of the autistic person was monitored in real-time, parallel to the performance's measurements, and through it the VR-based tasks were progressively adapted.
+
+\subsubsection{Structure of the trial}
+The system was divided into two subsystems, the \gls{as} and the \gls{ps} systems: the \gls{as} one adapts the tasks' level based on the performance of the subject and his anxiety level measured through the physiological indexes; the \gls{ps} one changes tasks' difficulty based only on the performance of the subject.
+
+While the participants were interacting with VR-based systems, their \gls{pr}, \gls{eda} and \gls{skt} signals, were acquired by an instruments called Biopac MP150 (from Biopac Systems Inc.) which operates in wireless mode with sampling frequency of 1 KHz.
+These signals were chosen because of their advantage of being measurable in a non-invasive way.
+
+To be specific, \gls{pr} was used since sympathetic nervous system has excitatory effects on cardiac functions and so it increases the heart rate; \gls{eda} and \gls{skt} on the other hand register the variations on the skin temperature and dryness caused by the vasoconstriction due to anxiety.\\
+
+During the participation to the VR-based tasks, the mean value of the participant's physiological indexes were estimated in a synchronized manner along with VR-based task progression; before the start of the real trial, a 3 min long period of time was dedicated to record physiological signals representing the normal state, in order to make a comparison with the altered signals that would have been taken in a second moment.
+Subsequently these indexes were given as inputs to an anxiety predictor which was based on fuzzy-logic for a more reliability when facing data uncertainty.
+
+Both \gls{as} and \gls{ps} systems had 12 social stories and relative tasks divided in three levels of difficulty.
+
+\subsubsection{Results}
+\label{sec:resultsVR}
+After the described experiment, some valuable conclusions have been drawn:
+\begin{itemize}
+\item The participants appreciated the interaction with the system and did not feel agitation when dealing with the physiological sensors, so this was a good index that such a system can be well accepted by the target population;
+\item The tasks were presented by a \gls{va} showing a happy expression in some cases, while an angry one in other cases and the anxiety measures revealed a slight increase in anxiety when the subjects were dealing with the angry face;
+\item The number of task trials that were successfully executed by the subjects was higher in the case of the \gls{as} system, this suggesting that \gls{as} system brought the participants to higher levels of challenge for a longer duration of time.
+The great implication of this is that the system could be a good solution for improving the skill training.
+\end{itemize}
+
+A lot of improvements still need to be done over this system: for example a further step can be adding an eye tracking tool in order to better understand on what the subject is focusing while looking at the \gls{va}, and so, if the aspect of the \gls{va} itself (like the expression on the face) can be a real reason of anxiety increase or reduction.
+Moreover, the system can make use of a technology different from the Biopac M150, which is expensive and offers the monitoring of parameters not really necessary for this type of project.
+
+Looking at the whole system it can be stated that this tool can allow a very useful didactic training procedure for people with \gls{asd}, and its potential affordability for normal families and relatively easy use make it a powerful solution in the research field  of \gls{asd}.
+\cri{forse devo essere più specifica nella parte in cui descrivo come il sistema as adatta le task all'ansia?}
+
 \section{Conclusions}\label{sec:conclusions}

### 2017-12-07 paper.tex
Added conclusions

@@
 
-With respect to these aims, this work is divided into two main sections: In \autoref{sec:diagnosis} we present some innovative tools and procedures to help diagnosing the syndrome in the first one or two years of a child; in \autoref{sec:thera_tech} we describe three \cri{vedere se poi il numero va bene} devices and methods useful for learning and improving cognitive skills.
+With respect to these aims, this work is divided into two main sections: In \autoref{sec:diagnosis} we present some innovative tools and procedures to help diagnosing the syndrome in the first one or two years of a child; in \autoref{sec:thera_tech} we describe two devices and methods useful for learning and improving cognitive skills.
 
@@
 
-Moreover, although normally it is not considered as a diagnostic criteria, motor impairment associated with ASD may have a significant impact on daily life tasks and, since up to 80\% of children with autism show motor anomalies highly correlated with the severity of social deficiency, hand-eye coordination could be considered as a new early diagnostic strategy for ASD syndrome \cite{Casellato2017}.
+Moreover, although normally it is not considered as a diagnostic criteria, motor impairment associated with ASD may have a significant impact on daily life tasks and, since up to 80\% of children with autism show motor anomalies highly correlated with the severity of social deficiency, hand-eye coordination could be considered as a new early diagnostic strategy for ASD syndrome \DP{Ho tolto la reference al primo paper, mi sembrava ridondante}.
 In fact, it has been suggested that sensory integration with bad timing brings to poor motor performance in children with ASD: the task of integrating multisensory input influences the forming of coherent perception, action coordination and planning.
@@
 
-Figures \ref{fig:task1} and \ref{fig:task1_pT} show the results just described.
+\autoref{fig:task1} and \autoref{fig:task1_pT} show the results just described.
 
@@
 
-Figure \ref{path} shows an example of trial with a TD child.
+Figure \autoref{path} shows an example of trial with a TD child.
 
@@
 \item the first task showed how children with \gls{asd} took longer to learn the task execution correctly, even though once the process had been assimilated the execution was correct, this meaning that these children showed a delayed ability to learn from sensory prediction errors; moreover the ASD child had more variability in motor execution, this suggesting more difficulty in maintaining performance consistency, and the gaze pattern was sticking less to the hand pattern if compared to the \gls{td} children.
-\item the second task showed how children with ASD obtained performance slightly worse than the TD children, but anyway they were able deploy the information regarding the previously assimilated path to improve the performance.
-This suggests that gls{asd} children are able to take advantage of the availability of the whole motor plan and supports the hypothesis that simple motor planning is intact but there is a diminished use of feedback.
+\item the second task showed how children with ASD obtained performance slightly worse than the TD children, but anyway they were able to deploy the information regarding the previously assimilated path to improve the performance.
+This suggests that \gls{asd} children are able to take advantage of the availability of the whole motor plan and supports the hypothesis that simple motor planning is intact but there is a diminished use of feedback.
 \end{itemize}
@@
 The signal processing passage consisted in low-pass filtering at 100 Hz, subsequent sampling at 256 Hz and digitization through 12-bit ADC.
-Finally.
-EEG signals were divided into 3 artifact-free epochs, subsequently filtered trough a Hamming window FIR band-pass filter.
+Finally, EEG signals were divided into 3 artifact-free epochs, subsequently filtered trough a Hamming window FIR band-pass filter.
 
@@
 \cri{forse devo essere più specifica nella parte in cui descrivo come il sistema as adatta le task all'ansia?}
+\DP{No secondo me quando hai spiegato che il sistema si adatta all'ansia e come rileva l'ansia, siamo apposto! Come hai fatto tu va benissimo!}
 
 \section{Conclusions}\label{sec:conclusions}
+All the presented experiments had reach good results while applied to subjects with \gls{asd}.
+This proofs that new technologies can be used, together with a specialized therapist, in the medical fields to prognosticate or manage the \gls{asd}.
+
+Unfortunately, before these tools are normally used in clinics and hospitals, it must takes a non-negligible amount of time and a lot of tests, but in a \textit{not-so-far} future, these techniques can help us to improve the life of the people affected by \gls{asd} and maybe they will allow us a better understanding of this desease.
 

### 2017-12-07 paper.tex
Approvate le conclusioni

@@
 
-Moreover, although normally it is not considered as a diagnostic criteria, motor impairment associated with ASD may have a significant impact on daily life tasks and, since up to 80\% of children with autism show motor anomalies highly correlated with the severity of social deficiency, hand-eye coordination could be considered as a new early diagnostic strategy for ASD syndrome \DP{Ho tolto la reference al primo paper, mi sembrava ridondante}.
+Moreover, although normally it is not considered as a diagnostic criteria, motor impairment associated with ASD may have a significant impact on daily life tasks and, since up to 80\% of children with autism show motor anomalies highly correlated with the severity of social deficiency, hand-eye coordination could be considered as a new early diagnostic strategy for ASD syndrome.
 In fact, it has been suggested that sensory integration with bad timing brings to poor motor performance in children with ASD: the task of integrating multisensory input influences the forming of coherent perception, action coordination and planning.
@@
 Looking at the whole system it can be stated that this tool can allow a very useful didactic training procedure for people with \gls{asd}, and its potential affordability for normal families and relatively easy use make it a powerful solution in the research field  of \gls{asd}.
-\cri{forse devo essere più specifica nella parte in cui descrivo come il sistema as adatta le task all'ansia?}
-\DP{No secondo me quando hai spiegato che il sistema si adatta all'ansia e come rileva l'ansia, siamo apposto! Come hai fatto tu va benissimo!}
 
 \section{Conclusions}\label{sec:conclusions}
-All the presented experiments had reach good results while applied to subjects with \gls{asd}.
-This proofs that new technologies can be used, together with a specialized therapist, in the medical fields to prognosticate or manage the \gls{asd}.
+All the presented experiments reached good results while applied to subjects with \gls{asd}: they prove that new technologies, together with a specialized therapist, can be used in the medical field to diagnose or manage the \gls{asd}.
 
-Unfortunately, before these tools are normally used in clinics and hospitals, it must takes a non-negligible amount of time and a lot of tests, but in a \textit{not-so-far} future, these techniques can help us to improve the life of the people affected by \gls{asd} and maybe they will allow us a better understanding of this desease.
+Unfortunately, it takes a non-negligible amount of time and several tests before these tools can be normally used in clinics and hospitals and the path is still long, but in a \textit{not-so-far} future these techniques will be able to help us improve the life of the people affected by \gls{asd} and maybe better understand this disease.
 

### 2017-12-14 paper.tex
Review Davide

@@
 \gls{asd} is a term used to cover a very big set of disorders.
-There are a lot of studies and experiments in this field, but still a lot questions about it are unresolved: for example, the symptoms are well known, while the causes are still mostly unknown.
+There are a lot of studies and experiments in this field, but still a lot questions about it are still not being solved \DP{Forse qui ci vanno i due punti :D}, for example, the symptoms are well known, while the causes are still mostly unknown.
 Nowadays \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered to a patient who is at least 3 years old.
@@
 
-With respect to these aims, this work is divided into two main sections: In \autoref{sec:diagnosis} we present some innovative tools and procedures to help diagnosing the syndrome in the first one or two years of a child; in \autoref{sec:thera_tech} we describe two devices and methods useful for learning and improving cognitive skills.
+With respect to these aims, this work is divided into two main sections: in \autoref{sec:diagnosis} we present some innovative tools and procedures to help diagnosing the syndrome in the first one or two years of a child; in \autoref{sec:thera_tech} we describe two devices and methods useful for learning and improving cognitive skills.
 
@@
 \subsubsection{Material and methods}
-In \cite{Casellato2017} the experimental set-up involved sixteen children aged between 8 and 10 years old and was composed by a haptic robotic manipulandum (Phantom Omni, Sensable-Geomagic) with a 3D printed pen-like handle, a control pc with a suited control algorithm running and a table-mounted screen Eye tracker T60 (Tobii) of $1280\times1024$ pixels.
+In \cite{Casellato2017} the experimental set-up involved 16 children aged between 8 and 10 years old and was composed by a haptic robotic manipulandum (Phantom Omni, Sensable-Geomagic) with a 3D printed pen-like handle, a control pc with a suited control algorithm running and a table-mounted screen Eye tracker T60 (Tobii) of $1280\times1024$ pixels.
 The manipulandum's sampling frequency was of 1 kHz, while the Eye Tracker's sampling frequency was of 60 Hz.
@@
 
-The actual trial consisted in two main tasks: the first task was about following a diagonal straight path moving an end-effector from a start square to an end square without exiting the path boundaries; in the second task a target moved on the screen following a curvilinear predefined path representing a digitalized version of the visuo-motor precision sub-task of the NEPSY-II protocol.
+The actual trial consisted in two main tasks: the first task was about following a diagonal straight path moving an end-effector from a start square to an end square without exiting the path boundaries; in the second task a target moved on the screen following a curvilinear predefined path representing a digitalized version of the visuo-motor precision sub-task of the NEPSY-II protocol \DP{Cos'è il NEPSY-II protocol?}.
 
@@
 \item during the first perturbed attempts the performance of the subjects were significantly low and attest a slow adaptation to the change;
-\item after some perturbed attempts the subjects eventually manage to compensate the force almost properly, with a progressive reduction in the product $pathL \dot T$ (where $pathL$ is the length of the path while $T$ is the time taken to travel through it);
+\item after some perturbed attempts the subjects eventually manage to compensate the force almost properly, with a progressive reduction in the product $pathL \cdot T$ (where $pathL$ is the length of the path while $T$ is the time taken to travel through it);
 \item when the attempts go back to be not-perturbated there is an initial overcompensation, which eventually is re-calibrated with even better performance than the ones obtained initially.
@@
 \includegraphics[width=\textwidth]{task1_pT.png}
-\caption{Task 1 pathLxT vs n of trials}
+\caption{Task 1 $pathL \cdot T$ vs number of trials}
 \label{fig:task1_pT}
@@
 
-During the second task there is a significant difference between \gls{td} (TD) children and children with ASD and between the first and the second attempt:
+During the second task there is a significant difference between \gls{td} children and children with ASD and between the first and the second attempt\DP{Il second task è strutturato come il primo?
+Come sono gli attempts?
+Non lo hai spiegato}:
 \begin{itemize}
-\item Even though there is not a strong correlation among the children of a same group, it can be noticed that both TD children and ASD children performed better during the second attempt, when they already knew the path to follow a priori;
+\item Even though there is not a strong correlation among the children of a same group, it can be noticed that both TD children and \gls{asd} children performed better during the second attempt, when they already knew the path to follow a priori;
 \item In general, \gls{td} children had better performance than \gls{asd} children;
-\item For ASD children, the \textit{hand-gaze} distance was higher than for TD children, but quite the same in both the attempts.
+\item For \gls{asd} children, the \textit{hand-gaze} distance was higher than for TD children, but quite the same in both the attempts.
 \end{itemize}
 
-Figure \autoref{path} shows an example of trial with a TD child.
+\autoref{path} shows an example of trial with a \gls{td} child.
 
@@
 \begin{itemize}
-\item the first task showed how children with \gls{asd} took longer to learn the task execution correctly, even though once the process had been assimilated the execution was correct, this meaning that these children showed a delayed ability to learn from sensory prediction errors; moreover the ASD child had more variability in motor execution, this suggesting more difficulty in maintaining performance consistency, and the gaze pattern was sticking less to the hand pattern if compared to the \gls{td} children.
+\item the first task showed how children with \gls{asd} took longer to learn the task execution correctly, even though once the process had been assimilated the execution was correct.
+This meaning that these children showed a delayed ability to learn from sensory prediction errors; moreover the ASD child had more variability in motor execution, this suggesting more difficulty in maintaining performance consistency, and the gaze pattern was sticking less to the hand pattern if compared to the \gls{td} children.
 \item the second task showed how children with ASD obtained performance slightly worse than the TD children, but anyway they were able to deploy the information regarding the previously assimilated path to improve the performance.
-This suggests that \gls{asd} children are able to take advantage of the availability of the whole motor plan and supports the hypothesis that simple motor planning is intact but there is a diminished use of feedback.
+This suggests that \gls{asd} children are able to take advantage of the availability of the whole motor plan and supports the hypothesis that simple motor planning ability is intact but there is a diminished use of feedback.
 \end{itemize}
@@
 Since then, multiple cases have been registered and so researchers started to look for associations between abnormal \gls{eeg} findings and individuals with \gls{asd}.
-This field is still mostly to be uncovered, since classification and evaluation of \gls{eeg} signals are limited for now, but recent studies suggest a feasible use of this diagnostic technique in the field of gls{asd} \cite{Behnam2008}.
+This field is still mostly to be uncovered, since classification and evaluation of \gls{eeg} signals are limited for now, but recent studies suggest a feasible use of this diagnostic technique in the field of \gls{asd} \cite{Behnam2008}.
 
@@
 Results show that the discriminating ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and \autoref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
-Moreover, \autoref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.
+Moreover, \autoref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $0.01 < p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.
 
@@
 
-%TODO Avatar-based techniques to improve the performances of the therapy
-%TODO Methods to detect the anxiety level
 To improve the performance of the sessions, the use of \gls{va} platforms has been introducted.
@@
 	\item[Attention Score] the child takes one point for each second he's looking at the robot’s face whenever the robot is asking him a question;
-	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and moment in which the child start answering the questions.
-	10 points are given for the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
+	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and the moment in which the child start answering the questions.
+	10 points are given within the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
 \end{LaTeXdescription}
@@
 After 20 minutes of session therapy, results are collected.
+
 This experiment has been done in five healthy male children and with three different type of interaction subject: an avatar programmed as said before, a pre-programmed robot and a therapist in a classical face-to-face session.
@@
 
-While the participants were interacting with VR-based systems, their \gls{pr}, \gls{eda} and \gls{skt} signals, were acquired by an instruments called Biopac MP150 (from Biopac Systems Inc.) which operates in wireless mode with sampling frequency of 1 KHz.
+While the participants were interacting with VR-based systems, their \gls{pr}, \gls{eda} and \gls{skt} signals, were acquired by an instruments called \textit{Biopac MP150} (from Biopac Systems Inc.) which operates in wireless mode with sampling frequency of 1 KHz.
 These signals were chosen because of their advantage of being measurable in a non-invasive way.
@@
 A lot of improvements still need to be done over this system: for example a further step can be adding an eye tracking tool in order to better understand on what the subject is focusing while looking at the \gls{va}, and so, if the aspect of the \gls{va} itself (like the expression on the face) can be a real reason of anxiety increase or reduction.
-Moreover, the system can make use of a technology different from the Biopac M150, which is expensive and offers the monitoring of parameters not really necessary for this type of project.
+Moreover, the system can make use of a technology different from the \textit{Biopac M150}, which is expensive and offers the monitoring of parameters not really necessary for this type of project.
 

### 2017-12-17 paper.tex
Revisionato report, aggiunta descrizione seconda task

@@
 
-Our aim is to analyze the current technology-based solutions that can help the therapist and the family of an autistic subject to interact with him.
+Our aim is to analyse the current technology-based solutions that can help the therapist and the family of an autistic subject to interact with him.
 These solutions exploit the joint use of human intelligence and artificial intelligence to improve
@@
 % TODO Brief presentation of ASD (?)
-\gls{asd} is a term used to cover a very big set of disorders.
-There are a lot of studies and experiments in this field, but still a lot questions about it are still not being solved \DP{Forse qui ci vanno i due punti :D}, for example, the symptoms are well known, while the causes are still mostly unknown.
+\gls{asd} is a term used to cover a very big set of disorders, there are a lot of studies and experiments in this field, but still a lot questions about it are still unsolved: for example the symptoms are well known, while the causes are still mostly unknown.
 Nowadays \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered to a patient who is at least 3 years old.
@@
 \label{sec:hand_eye}
-A different aspect to take into consideration when facing subjects with \gls{asd}, is the motor disorder related to the syndrome.
+An aspect to take into consideration when facing subjects with \gls{asd}, is the motor disorder related to the syndrome.
 In \cite{Casellato2017} a new approach to face the issue is presented, where the proposed protocol may be used for ad hoc subject training, helping children with ASD to enhance motor abilities related to hand-eye coordination.
@@
 
-The actual trial consisted in two main tasks: the first task was about following a diagonal straight path moving an end-effector from a start square to an end square without exiting the path boundaries; in the second task a target moved on the screen following a curvilinear predefined path representing a digitalized version of the visuo-motor precision sub-task of the NEPSY-II protocol \DP{Cos'è il NEPSY-II protocol?}.
+The actual trial consisted in two main tasks: the first task was about following a diagonal straight path moving an end-effector from a start square to an end square without exiting the path boundaries; in the second task a target moved on the screen following a curvilinear predefined path.
 
@@
 \item after some perturbed attempts the subjects eventually manage to compensate the force almost properly, with a progressive reduction in the product $pathL \cdot T$ (where $pathL$ is the length of the path while $T$ is the time taken to travel through it);
-\item when the attempts go back to be not-perturbated there is an initial overcompensation, which eventually is re-calibrated with even better performance than the ones obtained initially.
+\item when the attempts go back to be not-perturbed there is an initial overcompensation, which eventually is re-calibrated with even better performance than the ones obtained initially.
 \end{itemize}
@@
 
-During the second task there is a significant difference between \gls{td} children and children with ASD and between the first and the second attempt\DP{Il second task è strutturato come il primo?
-Come sono gli attempts?
-Non lo hai spiegato}:
+The second task was composed by three trials:
 \begin{itemize}
-\item Even though there is not a strong correlation among the children of a same group, it can be noticed that both TD children and \gls{asd} children performed better during the second attempt, when they already knew the path to follow a priori;
+\item the participant had to catch a moving target (a grey square) with the pen-like robot handle whose feedback was represented on the screen as a red square.
+In this case the moving target did not leave a trace while moving;
+\item this time the moving target was displayed on the screen together with its complete path, and the participant was asked to behave like in A);
+\item finally the subject was asked to track the same path at a self-paced velocity, without a displayed moving target.
+\end{itemize}
+In all trials, the inly visual feedback that the subject was provided with, was about the end-effector position on the screen. Moreover, both gaze and robot positions were recorded.
+
+During the second task there is a significant difference between \gls{td} children and children with ASD and between the first and the second attempt:
+\begin{itemize}
+\item Even though there is not a strong correlation among the children of a same group, it can be noticed that both TD children and \gls{asd} children performed better during the second attempt, when they already knew the path to follow a priori thanks to the track left behind the target;
 \item In general, \gls{td} children had better performance than \gls{asd} children;
@@
 
-If we unify the knowledge on the \gls{eeg} functioning principles, to the signal processing theory, we obtain a powerful diagnostic tool: representations based on Fourier Transform have been commonly applied and this brought to light that the \gls{eeg} spectrum contains five main frequency bands with characteristic waveforms and so the main way to highlight differences between normal subjects and autistic subjects can be to analyze the coherence of \gls{eeg} signals form different brain regions in order to find coupling among the signals in frequency domain.
+If we unify the knowledge on the \gls{eeg} functioning principles to the signal processing theory, we obtain a powerful diagnostic tool.
+Representations based on Fourier Transform have been commonly applied and this brought to light that the \gls{eeg} spectrum contains five main frequency bands with characteristic waveforms and so the main way to highlight differences between normal subjects and autistic subjects can be to analyse the coherence of \gls{eeg} signals form different brain regions in order to find coupling among the signals in frequency domain.
 
@@
 Results show that the discriminating ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and \autoref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
-Moreover, \autoref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $0.01 < p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.
+Moreover, \autoref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $0.01 < p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones.
+This observation sticks with the statements like the ones that Zilbovicius et al.
+and Alahbabi et al.
+made in \cite{Zilbovicius2000} \cite{ANA} about a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes.
 
@@
 \midrule
-Autism & 90.0 & 10.0\\
+Autism & 89.5 & 10.0\\
 Normal & 11.1 & 88.9\\
@@
 
-To improve the performance of the sessions, the use of \gls{va} platforms has been introducted.
+To improve the performance of the sessions, the use of \gls{va} platforms has been introduced.
 A \gls{va} platform consists of an Avatar, that can be a robot or a virtual character, a learning software that receives information from the Avatar, elaborates them and adjusts the response of the Avatar, and an interface for the therapist that interprets the results.
@@
 The first solution was proposed in \cite{Alahbabi17}, using a robotic Avatar.
-They chose a robotic-based solution since it has been shown in \cite{Pioggia08} that patients manifest a more favorable response towards humanoid robots than to other non-humanoid virtual characters.
+They chose a robotic-based solution since it has been shown in \cite{Pioggia08} that patients manifest a more favourable response towards humanoid robots than to other non-humanoid virtual characters.
 
@@
 \begin{itemize}
-	\item most of the robotic or virtualized therapies are preprogrammed and this makes the session boring and repetitive;
+	\item most of the robotic or virtualized therapies are pre-programmed and this makes the session boring and repetitive;
 	\item robots are limited and work in a controlled environment;
@@
 
-In this work they try to fulfill these lacks using a set of advanced technology tools, specifically a \textit{NAO Robot} (visible in \autoref{fig:nao_robot}) and a Perception Neuron Set of 32 sensors.
+In this work they try to fulfil these lacks using a set of advanced technology tools, specifically a \textit{NAO Robot} (visible in \autoref{fig:nao_robot}) and a Perception Neuron Set of 32 sensors.
 
@@
 
-During the whole process a heart-rate measuring band is worn by the partecipant, to monitor the partecipant's level of anxiety and stop or change the session whenever an intervention is required.
+During the whole process a heart-rate measuring band is worn by the participant, to monitor the participant's level of anxiety and stop or change the session whenever an intervention is required.
 
@@
 
-The movements performed by the robot and imitated by the child and the therapist's questions are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.
+The movements performed by the robot and imitated by the child and the therapist's questions are specifically selected to teach the child how to interact with other people and to improve his response to social stimulus.
 
